si: code and prose exploring Spatial Interaction models

### 2022-04-15 README.qmd

---
# format: html
format: gfm
number-sections: true
title: "si: code and prose exploring Spatial Interaction models"
bibliography: data-raw/references.bib
execute:
  cache: true
---

>>>>

---
# format: html
format: gfm
number-sections: true
title: "si: code and prose exploring Spatial Interaction models"
bibliography: data-raw/references.bib
execute:
  cache: true
  fig.path: "man/figures/README-"
---
